MLCommons Earthquake Science Benchmark

### 2022-02-19 paper-capstone-earthquake.tex
sync
capstone

\documentclass[sigplan,screen]{format/acmart}
\usepackage{todonotes}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[pdf]{graphviz}
\usepackage{xpatch}
\usepackage{adjustbox}
\usepackage{makecell} 
\usepackage{ifthen}

@@

\acmConference[T. Buttler, R. Knuuti, J, Kolesar, Geoffrey C. Fox, Gregor von Laszewski, J. Fox, University of Virginia Data Science Capstone 2022]{MLCommons Earthquake Science Benchmark}{Jan. 22 -- Aug. 31 2022}{Charlotsville, VA, US}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  June 03--05, 2018, Woodstock, NY} 
\acmPrice{}
\acmISBN{}
%%\acmSubmissionID{123-A56-BU3}
%%\citestyle{acmauthoryear}

\makeatletter
\newcommand*{\addFileDependency}[1]{% argument=file name and extension
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother
\xpretocmd{\digraph}{\addFileDependency{#2.dot}}{}{}
% Removes margin issue
% TODO - remove this line when we're ready to submit
\setlength{\marginparwidth}{2cm}
\begin{document}

@@

\author{Thomas Butler}
\orcid{0000-0003-1515-0098}
\affiliation{%
  \institution{University of Virginia}
  \streetaddress{TBD}
  \city{Charlotsville, VA}
  \country{USA}}
 \email{Tommysbutler@gmail.com}

\author{Robert Knuuti}
\orcid{0000-0003-2614-0899}
\affiliation{%
  \institution{University of Virginia}
  \streetaddress{TBD}
  \city{Charoletteville}
  \country{USA}}
\email{robert.knuuti@gmail.com}

\author{Jake Kolessar}
\affiliation{%
  \institution{University of Virginia}
  \streetaddress{TBD}
  \city{Charoletteville}
  \country{United States}}
\email{jakekolessar@gmail.com}

\author{Geoffrey C. Fox}
\affiliation{%
  \institution{University of Virginia}
  \streetaddress{TBD}
  \city{Charlotsville, VA}
  \country{USA}}
\email{gcfexchange@gmail.com}

\author{Gregor von Laszewski}
\orcid{0000-0001-9558-179X}
\affiliation{%
  \institution{University of Virginia}
  \streetaddress{TBD}
  \city{Charlotsville, VA}
  \country{USA}}
\email{laszewski@gmail.com}

\author{Judy Fox}
\affiliation{%
  \institution{University of Virginia}
  \streetaddress{TBD}
  \city{Charlotsville, VA}
  \country{USA}}
\email{cwk9mp@virginia.edu}

\renewcommand{\shortauthors}{Butler, Knuuti, Kolesar, Fox, von Laszewski}

@@

\newcommand{\nvidia}[1]{
    \ifthenelse{\equal{#1}{A100}}{\href{https://www.nvidia.com/en-us/data-center/a100/}{NVIDIA #1}}{} 
    \ifthenelse{\equal{#1}{V100}}{\href{https://www.nvidia.com/en-us/data-center/a100/}{NVIDIA #1}}{}
    \ifthenelse{\equal{#1}{K80}}{\href{https://www.nvidia.com/en-gb/data-center/tesla-k80/}{NVIDIA #1}}{}
    \ifthenelse{\equal{#1}{P100}}{\href{https://www.nvidia.com/en-us/data-center/tesla-p100/}{NVIDIA #1}}{}
    \ifthenelse{\equal{#1}{RTX3090}}{\href{https://www.nvidia.com/en-us/geforce/graphics-cards/30-series/rtx-3090/}{NVIDIA #1}}{}
    \ifthenelse{\equal{#1}{RTX2080TI}}{\href{https://www.nvidia.com/en-us/data-center/tesla-p100/}{NVIDIA #1}}{}

%\newcommand{\nvidiaV}{\href{https://www.nvidia.com/en-us/data-center/v100/}{NVIDIA V100}}

\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:my_label}
    \centering
%\begin{adjustbox}{angle=90}
\begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|r|l|ll|r|l|l|l|l|l|}
        \hline
        Section & Organization   & Machine                         & & Processors    & GPUs             & \makecell{Memory\\/Device} &  \makecell{GPU\\/Device} & \makecell{No. of\\ nodes} & Commissioned \\ 
        \hline
        \hline
         \ref{id:anl}   & ANL    & Aurora & \cite{www-aurora}         &              &                  & & & &    ??? 2022   \\ \hline
         \ref{id:ornl}  & ORNL   & Summit &\cite{www-summit}         &        27000 & NVIDIA Volta     & & & &               \\ \hline
         \ref{id:nersc} & NERSC  & Perlmutter & \cite{www-perlmutter} &         6000 & \nvidia{A100}      & & & & Jan 2022      \\ \hline
         \ref{id:sdsc}  & SDSC   & Expanse & \cite{www-expanse}       &          200 & NVIDIA V100 SMX2 & & & &               \\ \hline
         \ref{id:uva}   & UVA    & Rivanna &\cite{www-rivanna}       &            8 & \nvidia{A100}      & 80GB & ? & &  Feb 2022      \\
            &    &  &       &            8 & \nvidia{A100}      & 40GB & 8 & &       \\
            &    &  &       &            ? & \nvidid{RTX3090}   & 24GB & ? & ? & 2021          \\
            &    &  &       &            ? & \nvidia{K80}       & 11GB & 8 & 9 & 2021          \\
            &    &  &       &            ? & \nvidia{V100}      & 16GB & 4 & 1 & 2021          \\
            &    &  &       &            ? & \nvidia{V100}      & 32GB & 4 & 12 & 2021          \\
            &    &  &       &            ? & \nvidia{P100}      & 12GB & 4 & 3 & 2021          \\
            &    &  &       &            ? & \nvidia{RTX2080TI} & 11GB & 10 & 2 & 2021          \\
         \hline
         \ref{id:ral}   & RAL    & Pearl &\cite{www-pearl-1}         &           16 & \nvidiaV      & & & &  \\ \hline
         \ref{id:dgx}   & Fox    & DGX Station A100 &\cite{www-dgx-station-a100} & 4 & \nvidiaA      & 80GB & 4 & 1 & May 2021      \\
         \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

@@

{\bf Thomas Butler}
is a Graduate Student at University of Virginia's School of Data Science. His undergraduate degree is in Biomedical engineering. He has over 8 years of experience in the Infertility field helping patients, jointly running a Andrology lab, and contributing research to advance the field through joint research on how AMH effects pregnancy outcomes and sperm antibodies effect PSA. He has a certificate in Data Analytics from Georgia Institute of Technology.

>>>>

\PassOptionsToPackage{hyphens}{url}
\documentclass[sigplan,screen]{format/acmart}
\usepackage{todonotes}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[pdf]{graphviz}
\usepackage{xpatch}
\usepackage{adjustbox}
\usepackage{makecell} 
\usepackage{ifthen}
\usepackage[numbers]{natbib}‎

\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}

@@

%\acmConference[T. Buttler, R. Knuuti, J, Kolesar, G. C. Fox,
%  G. von Laszewski, J. Fox, University of Virginia Data Science
%  Capstone 2022]{MLCommons Earthquake Science Benchmark}{Jan. 22 --
%  Aug. 31 2022}{Charlotsville, VA, USA}

\acmConference[Data Science
  Capstone, University of Virginia, 2022]{MLCommons Earthquake Science Benchmark}{Jan. 22 --
  Aug. 31 2022}{Charlotsville, VA, USA}

\acmBooktitle{Woodstock '18:
  ACM Symposium on Neural Gaze Detection, June 03--05, 2018,
  Woodstock, NY}

\acmPrice{}
\acmISBN{}
%%\acmSubmissionID{123-A56-BU3}
%%\citestyle{acmauthoryear}

\makeatletter
\newcommand*{\addFileDependency}[1]{% argument=file name and extension
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother
\xpretocmd{\digraph}{\addFileDependency{#2.dot}}{}{}

\begin{document}

@@

\author{Thomas Butler}
\orcid{0000-0003-1515-0098}
\affiliation{%
  \institution{University of Virginia}
  \city{Charoletteville}
  \country{USA}}
 \email{Tommysbutler@gmail.com}

\author{Robert Knuuti}
\orcid{0000-0003-2614-0899}
\affiliation{%
  \institution{University of Virginia}
  \city{Charoletteville}
  \country{USA}}
\email{robert.knuuti@gmail.com}

\author{Jake Kolessar}
\affiliation{%
  \institution{University of Virginia}
  \city{Charlottesville}
  \state{VA}
  \postcode{22911}
  \country{United States}}
\email{jakekolessar@gmail.com}

\author{Geoffrey C. Fox}
\affiliation{%
  \institution{University of Virginia}
  \streetaddress{Biocomplexity Institute
Town Center Four
994 Research Park Boulevard}
  \city{Charlottesville}    
  \state{VA}
  \postcode{22911}
  \country{USA}}
\email{gcfexchange@gmail.com}

\author{Gregor von Laszewski}
\orcid{0000-0001-9558-179X}
\affiliation{%
  \institution{University of Virginia}
  \streetaddress{Biocomplexity Institute
Town Center Four
994 Research Park Boulevard}
  \city{Charlottesville}    
  \state{VA}
  \postcode{22911}
  \country{USA}}
\email{laszewski@gmail.com}

\author{Judy Fox}
\affiliation{%
  \institution{University of Virginia}
  \city{Charlottesville}      
  \state{VA}
  \postcode{22911}
  \country{USA}}
\email{cwk9mp@virginia.edu}

\renewcommand{\shortauthors}{Butler, Knuuti, Kolesar, G Fox, G von Laszewski}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% THIS SECTION MAY NOT BE COPIED INTO ANOTHER PAPER WITHOUT MAKING GREGOR VON LASZEWSKI COAUTHOR
%
%
\newcommand{\nvidia}[1]{
\ifthenelse{\equal{#1}{A100}}{\href{https://www.nvidia.com/en-us/data-center/a100/}{NVIDIA #1}}{}%
\ifthenelse{\equal{#1}{V100}}{\href{https://www.nvidia.com/en-us/data-center/a100/}{NVIDIA #1}}{}%
\ifthenelse{\equal{#1}{K80}}{\href{https://www.nvidia.com/en-gb/data-center/tesla-k80/}{NVIDIA #1}}{}%
\ifthenelse{\equal{#1}{P100}}{\href{https://www.nvidia.com/en-us/data-center/tesla-p100/}{NVIDIA #1}}{}%
\ifthenelse{\equal{#1}{RTX3090}}{\href{https://www.nvidia.com/en-us/geforce/graphics-cards/30-series/rtx-3090/}{NVIDIA #1}}{}%
\ifthenelse{\equal{#1}{RTX2080TI}}{\href{https://www.nvidia.com/en-eu/geforce/20-series/}{NVIDIA #1}}{}%
\ifthenelse{\equal{#1}{Volta}}{\href{https://www.nvidia.com/en-us/data-center/volta-gpu-architecture/}{NVIDIA #1}}{}%
}
%\newcommand{\nvidiaV}{\href{https://www.nvidia.com/en-us/data-center/v100/}{NVIDIA V100}}

\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:my_label}
    \centering
%\begin{adjustbox}{angle=90}
\begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|r|l|ll|r|l|l|l|l|l|}
        \hline
        Section & Organization   & Machine                         & & Processors    & GPUs             & \makecell{Memory\\/Device} &  \makecell{GPU\\/Device} & \makecell{No. of\\ nodes} & Commissioned \\ 
        \hline
        \hline
         \ref{id:anl}   & ANL    & Aurora & \cite{www-aurora}         &              &                  & & & &    ??? 2022   \\ \hline
         \ref{id:ornl}  & ORNL   & Summit &\cite{www-summit}         &        27000 & \nvidia{volta}     & & & &               \\ \hline
         \ref{id:nersc} & NERSC  & Perlmutter & \cite{www-perlmutter} &         6000 & \nvidia{A100}      & & & & Jan 2022      \\ \hline
         \ref{id:sdsc}  & SDSC   & Expanse & \cite{www-expanse}       &          200 & \nvidid{V100}
         SMX2 & & & &               \\ \hline
         \ref{id:uva}   & UVA    & Rivanna &\cite{www-rivanna}       &            8 & \nvidia{A100}      & 80GB & ? & &  Feb 2022      \\
            &    &  &       &            8 & \nvidia{A100}      & 40GB & 8 & &       \\
            &    &  &       &            ? & \nvidid{RTX3090}   & 24GB & ? & ? & 2021          \\
            &    &  &       &            ? & \nvidia{K80}       & 11GB & 8 & 9 & 2021          \\
            &    &  &       &            ? & \nvidia{V100}      & 16GB & 4 & 1 & 2021          \\
            &    &  &       &            ? & \nvidia{V100}      & 32GB & 4 & 12 & 2021          \\
            &    &  &       &            ? & \nvidia{P100}      & 12GB & 4 & 3 & 2021          \\
            &    &  &       &            ? & \nvidia{RTX2080TI} & 11GB & 10 & 2 & 2021          \\
         \hline
         \ref{id:ral}   & RAL    & Pearl &\cite{www-pearl-1}         &           16 & \nvidia{V100}      & & & &  \\ \hline
         \ref{id:dgx}   & Fox    & DGX Station A100 &\cite{www-dgx-station-a100} & 4 & \nvidia{A100}      & 80GB & 4 & 1 & May 2021      \\
         \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

%
% THIS SECTION MAY NOT BE COPIED INTO ANOTHER PAPER WITHOUT MAKING GREGOR VON LASZEWSKI COAUTHOR
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{ACM-Reference-Format}
\bibliography{paper-capstone-earthquake}

@@

{\bf Thomas Butler}
is a Graduate Student at University of Virginia's School of Data Science. His undergraduate degree is in Biomedical engineering. He has over eight years of experience in the Infertility field helping patients, jointly running a Andrology lab, and contributing research to advance the field through joint research on how AMH effects pregnancy outcomes and sperm antibodies effect PSA. He has a certificate in Data Analytics from Georgia Institute of Technology.
